On Math

### 2025-04-24 cards/paper.tex
function graphs and more changes!
- complex numbers - general description, powers of i, magnitude etc
- add couple notes at the beginning
- create a sandbox at the end of the document to save imprtant notes
- couple stylistic changes

\documentclass{article}
\usepackage{amsmath,amssymb,amsthm,textcomp,mathtools}

@@

@@

\section{Complex numbers}
\subsection{Argument of a complex number}
There is natural angle $\theta$ that \textit{z} makes with real x-axis. This angle is called \textit{the argument of z}. The numeric value of $arg(z)$ is given in radians and also
\begin{equation}
0 \leq arg(z) \leq 2\pi
\end{equation}

@@

\subsection{Reciprocal functions}
\begin{equation}
  f(x) = \frac{1}{x}
\end{equation}

% TODO: not range?
Domain of (transformed) reciprocal function
\begin{equation}
f(x) = \frac{a}{bx+c} + d
\end{equation}
has the horizontal asymptote $y = d$ therefore the range is
\begin{equation}
f(x) = \in (-\infty, d) \cup (d, \infty)
\end{equation}

% TODO: range
Range of (transformed) reciprocal function
\begin{equation}
f(x) = \frac{a}{bx+c} + d
\end{equation}
has the vertical asymptote $y = d$ therefore the range is
\begin{equation}
f(x) = \in (-\infty, d) \cup (d, \infty)
\end{equation}

@@

Example with changing base:
\begin{equation}
  \begin{gathered}
  \log_ax = \frac{\ln x}{\ln a}
  \frac{d}{dx}(\log_ax) = \frac{d}{dx}(\frac{\ln x}{\ln a}) =
  = \frac{1}{\ln a} * \frac{d}{dx}(\ln x) =
  = \frac{1}{\ln a} * \frac{1}{x} = \frac{1}{x\ln a}
  \end{gathered}
\end{equation}
\subsection{Chain rule for logarithmic function}
\begin{equation}
  \begin{gathered}
  y = \ln(2x+1)
  y = \ln u
  u = 2x+1
  y' = \frac{1}{u}
  u' = 2
  \frac{dy}{dx} = \frac{1}{u} * 2 = \frac{2}{u} = \frac{2}{2x+1}
  \end{gathered}
\end{equation}

\section{Integrals}
Also called \textit{antiderivatives}. To represent integrals we use an integral
symbol.

For example:

\begin{equation}
  \int 2x dx = x^2 + C
\end{equation}

Integrals like this are called 'indefinite integrals' and (in this case)
function being integrated is called an 'integrand'.

Integral of a sum of functions
\begin{equation}
  \int f(x) \pm g(x) \, dx = \int f(x) \, dx \pm \int g(x) \, dx
\end{equation}

Integral of a reciprocal function
\begin{equation}
  \int \frac{1}{x} \, dx = \int \ln abs(x) + C
\end{equation}
and also:
\begin{equation}
  \int \frac{1}{x} \, dx = \int \ln|x| + C = \ln abs(x) + \ln K = \ln (K (abs(x))
\end{equation}

Integral of an exponential function
\begin{equation}
  \int e^x \, dx = e^x + C
\end{equation}
with general base we know that
\begin{equation}
  \frac{d}{dx} (a^x) = a^x \ln a
\end{equation}
so reversing:
\begin{equation}
  \int a^x \, dx = \frac{a^x}{\ln a} + C
\end{equation}

Power rule for differentiation in reverse:
\begin{equation}
  \frac{d}{dx}(x^{n+1}) = (n+1)x^n
\end{equation}
same as:
\begin{equation}
  \int x^ndx = \frac{x^{n+1}}{n+1}
\end{equation}

Note: power rule does not work if $n=-1$

Marked integral for future
\begin{equation}
  \int_{a}^{b} f(x) \, dx
\end{equation}

>>>>

\documentclass{article}

\usepackage{amsmath,amssymb,amsthm,textcomp,mathtools}

\usepackage{tikz}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}

@@

\section{General notes and todos}
- I feel like multiline equations should have higher vertical spacing
- Trigonometry values can be done in a single table

@@

\section{Complex numbers}
Complex numbers can be represented by the point $(x, y)$ where $x$ is real axis and $y$
is imaginary axis. We call this plane as a 'complex plane', also called 'Argand diagram',
denoted as $C$.

\subsection{Powers of $i$}
\begin{equation}
  \begin{gathered}
    i^1 = \sqrt{-1} \\
    i^2 = (\sqrt{-1})^2 = -1 \\
    i^3 = -1 * i = -i \\
    i^4 = (-1) * (-1) = 1
  \end{gathered}
\end{equation}
and so on...

\subsection{Magnitude of a complex number}
The magnitude of a complex number is its distance from the origin $(0, 0)$.
It is denoted az $|z|$. For complex number $z = a + bi$ magnitude is:
\begin{equation}
  |z| = \sqrt{a^2 + b^2}
\end{equation}

\subsection{Argument of a complex number}
There is natural angle $\theta$ that \textit{z} makes with real x-axis. This angle is called \textit{the argument of z}. The numeric value of $arg(z)$ is given in radians and also
\begin{equation}
0 \leq arg(z) \leq 2\pi
\end{equation}

@@

\subsection{Reciprocal functions}

\begin{figure}
\centering
\begin{tikzpicture}
\begin{axis}[
    axis lines=center,
    xlabel=$x$,
    ylabel=$y$,
    title={Reciprocal Function $f(x) = \frac{1}{x}$},
    xmin=-5, xmax=5,
    ymin=-3, ymax=3,
    xtick={-5,-4,-3,-2,-1,1,2,3,4,5},
    ytick={-3,-2,-1,1,2,3},
    grid=both,
    domain=-5:5,
    samples=200,
    restrict y to domain=-3:3,
]
% Plot the function, excluding the region around x=0
\addplot[blue, thick] {1/x};

% Add asymptotes
\draw[dashed, red] (axis cs:0,-3) -- (axis cs:0,3);
\draw[dashed, red] (axis cs:-5,0) -- (axis cs:5,0);
\end{axis}
\end{tikzpicture}
\caption{Graph of the reciprocal function $f(x) = \frac{1}{x}$}
\end{figure}

%TODO: image
\begin{equation}
  f(x) = \frac{1}{x}
\end{equation}
When function is not transformed, it passes through points $(-1, -1)$ and $(1, 1)$.
% TODO: not range?
Domain of (transformed) reciprocal function
\begin{equation}
f(x) = \frac{a}{bx+c} + d
\end{equation}
has the horizontal asymptote $y = d$ therefore the range is
\begin{equation}
f(x) = \in (-\infty, d) \cup (d, \infty)
\end{equation}
% TODO: range
Range of (transformed) reciprocal function
\begin{equation}
f(x) = \frac{a}{bx+c} + d
\end{equation}
has the vertical asymptote $y = d$ therefore the range is
\begin{equation}
f(x) = \in (-\infty, d) \cup (d, \infty)
\end{equation}

@@

Example with changing base:
\begin{equation}
  \begin{gathered}
  \log_ax = \frac{\ln x}{\ln a} \\
  \frac{d}{dx}(\log_ax) = \frac{d}{dx}(\frac{\ln x}{\ln a}) = \\
  = \frac{1}{\ln a} * \frac{d}{dx}(\ln x) = \\
  = \frac{1}{\ln a} * \frac{1}{x} = \frac{1}{x\ln a}
  \end{gathered}
\end{equation}
\subsection{Chain rule for logarithmic function}
\begin{equation}
  \begin{gathered}
  y = \ln(2x+1) \\
  y = \ln u \\
  u = 2x+1 \\
  y' = \frac{1}{u} \\
  u' = 2 \\
  \frac{dy}{dx} = \frac{1}{u} * 2 = \frac{2}{u} = \frac{2}{2x+1}
  \end{gathered}
\end{equation}

\section{Integrals}
Also called \textit{antiderivatives}. To represent integrals we use an integral
symbol. For example:
\begin{equation}
  \int 2x dx = x^2 + C
\end{equation}
Integrals like this are called 'indefinite integrals' and (in this case)
function being integrated is called an 'integrand'.

\subsection{Integral of a sum of functions}
\begin{equation}
  \int f(x) \pm g(x) \, dx = \int f(x) \, dx \pm \int g(x) \, dx
\end{equation}

\subsection{Integral of a reciprocal function}
\begin{equation}
  \int \frac{1}{x} \, dx = \int \ln abs(x) + C
\end{equation}
and also:
\begin{equation}
  \int \frac{1}{x} \, dx = \int \ln|x| + C = \ln abs(x) + \ln K = \ln (K (abs(x))
\end{equation}

\subsection{Integral of an exponential function}
\begin{equation}
  \int e^x \, dx = e^x + C
\end{equation}
with general base we know that
\begin{equation}
  \frac{d}{dx} (a^x) = a^x \ln a
\end{equation}
so reversing:
\begin{equation}
  \int a^x \, dx = \frac{a^x}{\ln a} + C
\end{equation}

\subsection{Power rule for differentiation in reverse}
\begin{equation}
  \frac{d}{dx}(x^{n+1}) = (n+1)x^n
\end{equation}
same as:
\begin{equation}
  \int x^ndx = \frac{x^{n+1}}{n+1}
\end{equation}
Note: power rule does not work if $n=-1$!

\section{Sandbox}
Marked integral for future
\begin{equation}
  \int_{a}^{b} f(x) \, dx
\end{equation}
